Final paper: Towards Proving Termination of \texttt{zelda-mosaic} Algorithms under Conditions on the Input

### 2021-05-03 paper/paper.tex
paper: abstract

\begin{abstract}
    We report on a study of previous set of algorithms that we developed for
    building mosaics, implemented in \matlab\@. In particular, we are interested
    in the formalization of the algorithms and the relevant \matlab\ structures
    in Coq~\cite{Coq} and the termination of these algorithms under appropriate
    to-be-determined conditions. We present details on the algorithms along with
    our motivations for studying them. We then discuss an initial foray into
    related work. Next, we show an updated timeline for our progress. Lastly, we
    briefly identify the major contributions of each author to this proposal.
\end{abstract}

>>>>

\begin{abstract}
    We report on the development developing matrix algorithms in Coq intended to
    serve proofs about a subset of \matlab\@. Specifically, we are interested in
    a previous set of algorithms that we developed for building mosaics,
    implemented in \matlab\@. We discuss the formalization of the necessary
    matrix algorithms and the relevant \matlab\ structures in Coq~\cite{Coq}, as
    well as what remains to be done to prove the termination of the mosaic
    algorithms under appropriate to-be-determined conditions. We present details
    on the matrix development along with the key theorems for its correctness.
    We describe the challenges we faced in developing the matrix type and its
    operations, providing a glimpse at dependently-typed vectors in Coq. We also
    briefly discuss advanced automation in Coq useful for the matrix
    development.
\end{abstract}
